msc dissertation

### 2021-08-09 msc dissertation code.Rmd
latest

###find out the number of participants (obs) for each attention check level
attention1 <- subset(pennystudy2r1, dummycheck %in% c("1","2","3"))
attention2 <- subset(pennystudy2r1, dummycheck %in% c("2","3"))
attention3 <- subset(pennystudy2r1, dummycheck %in% c("3"))
```

@@

lm1 <- lm(measurement ~ headlineveracity + headlineveracity*condition, data = pennys2r1long_nona)
summary(lm1)

@@

pennys2r1a2cohen <- subset(pennystudy2r1, dummycheck %in% c("2","3"))
pennys2r1a2cohenc <- subset(pennys2r1a2cohen, condition %in% c("0"))
pennys2r1a2cohent <- subset(pennys2r1a2cohen, condition %in% c("1"))

cohen.d(pennys2r1a2cohenc$Fake, pennys2r1a2cohenc$Real, na.rm = TRUE)
cohen.d(pennys2r1a2cohent$Fake, pennys2r1a2cohent$Real, na.rm = TRUE)

#condition vs measurement

pennys2r1a2cohenc <- subset(pennys2r1longa2, condition %in% c("0"))
pennys2r1a2cohent <- subset(pennys2r1longa2, condition %in% c("1"))

cohen.d(pennys2r1a2cohenc$condition, pennys2r1a2cohenc$measurement, na.rm = TRUE)
cohen.d(pennys2r1a2cohent$condition, pennys2r1a2cohent$measurement, na.rm = TRUE)

## use glm, stepwise approach to see how each factor explaining the sharing intention. The family for the model is binomial since the dependent variable is dichotomous.
glm0 <- glm(measurement ~ 1, data = pennys2r1long_nona, family = binomial(link = "logit"))

@@

glm2 <- glm(measurement ~ condition + attentioncheck, data = pennys2r1long_nona, family = binomial(link = "logit"))

glm3 <- glm(measurement ~ condition + attentioncheck + headlineveracity, data = pennys2r1long_nona, family = binomial(link = "logit"))

glm4 <- glm(measurement ~ condition + attentioncheck +condition* headlineveracity, data = pennys2r1long_nona, family = binomial(link = "logit"))

anova(glm0,glm1,glm2,glm3,glm4,test='LR')

##looking at summary glm4, it is cleat that condition does not have a significant effect on measurement
summary(glm6)

glm5 <- glm(measurement ~ attentioncheck +condition* headlineveracity, data = pennys2r1long_nona, family = binomial(link = "logit"))
glm6 <- glm(measurement ~ headlineveracity + attentioncheck +condition* headlineveracity, data = pennys2r1long_nona, family = binomial(link = "logit"))

summary(glm7)

##maybe a mixed effect models?
#create a new column that recode item number from fake to real to 1-30, with 1-15 indicate fake, 16-30 indicate real

@@

#model 1, item_id indicates repeated measurements for each item
mult1 <- lmer (measurement ~ condition + attentioncheck + headlineveracity + (1|item_id),
             data = pennys2r1long)
summary(mult1)

@@

### graph 1: including all
```{r, message=FALSE}

@@

#Since the plot not specify which condition they use, then I need to plot all 4 graph in different condition

#condition 1: all

@@

ggplot(p1, aes(x = condition, y = as.numeric(percent), fill = headlineveracity)) + 
  geom_bar(stat = 'identity',position = 'dodge') + 
  geom_text(
    aes(label = as.numeric (percent)), vjust = 1.5, position = position_dodge(0.9))
```
### graph 2 attention check above and equal to 1

>>>>

###find out the number of participants (obs) for each attention check level
attention1 <- subset(pennys2r1long_nona, attentioncheck %in% c("1","2","3"))
attention2 <- subset(pennys2r1long_nona, attentioncheck %in% c("2","3"))
attention3 <- subset(pennys2r1long_nona, attentioncheck %in% c("3"))

## relase I should not dichotomise the scale as it loses info and reduces the power.
```{r, message=FALSE}
#recreate a data frame that does not rescale the data to either 0,1 but from 0 to 1,so divided each value by rating = (rating - 1)/5

pennystudy2r1nodi <- pennycook2 %>% 
  select (c(1, 210, 211, 212, 213, 214, 215, 216, 217, 218, 219, 220, 221, 222, 223, 224, 225, 226, 227, 228, 229, 230, 231, 232, 233, 234, 235, 236, 237, 238, 239, 2, 3, 4, 57, 60, 250, 252, 284,))

#successful screen1 test (result = 2)
pennystudy2r1nodi['screen1']=pennystudy2r1nodi['screen1_4'] + pennystudy2r1nodi['screen1_7']

#successful screen2 test (result = 2)
pennystudy2r1nodi['screen2']=pennystudy2r1nodi['screen2_3'] + pennystudy2r1nodi['screen2_5']

#successful screen3 test (result = 3)
pennystudy2r1nodi['screen3'] = na_if(pennystudy2r1nodi$screen3_2,1)
pennystudy2r1nodi['screen3'] = na_if(pennystudy2r1nodi$screen3,2)
pennystudy2r1nodi['screen3'] = na_if(pennystudy2r1nodi$screen3,4)
pennystudy2r1nodi['screen3'] = na_if(pennystudy2r1nodi$screen3,5)
#check if screen 3 successful
mean(pennystudy2r1nodi$screen3, na.rm = TRUE)

#re-code screen test: replace 2 and 3 to 1
pennystudy2r1nodi["screen1"][pennystudy2r1nodi["screen1"] == 2] <- 1
pennystudy2r1nodi["screen2"][pennystudy2r1nodi["screen2"] == 2] <- 1
pennystudy2r1nodi["screen3"][pennystudy2r1nodi["screen3"] == 3] <- 1

#re-code condition control = 0 treatment = 1
pennystudy2r1nodi["condition"][pennystudy2r1nodi["condition"] == 1] <- 0
pennystudy2r1nodi["condition"][pennystudy2r1nodi["condition"] == 2] <- 1

pennystudy2r1nodi[c("screen1","screen2","screen3")][is.na(pennystudy2r1nodi[c("screen1","screen2","screen3")])] <- 0

#create dummy column, add screen 1,2,3 together. Screen = 3 indicate success in all attention check
pennystudy2r1nodi['dummycheck']=pennystudy2r1nodi['screen1'] + pennystudy2r1nodi['screen2'] + pennystudy2r1nodi['screen3']

#like the researcher did, change data frame from wide to long
##first drop unnecessary column
colnames(pennystudy2r1nodi)

pennys2r1longnodi <- subset(pennystudy2r1nodi, select = c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20,21,22,23,24,25,26,27,28,29,30,31,32,33,34,43))

##Add ID column
pennys2r1longnodi <- tibble::rowid_to_column(pennys2r1longnodi, "ID")

pennys2r1longnodi <- gather_(pennys2r1longnodi, keycol, valuecol, gathercols)

merge(pennystudy2r1nodi, pennys2r1longnodi, by.x='condition', by.y='ID')

##organize data by ID, then reorder the column
pennys2r1longnodi <- pennys2r1longnodi[order(pennys2r1longnodi$ID),]

pennys2r1longnodi <- pennys2r1longnodi[, c(1, 2, 7, 8, 6, 5, 4, 3)]

##change dummycheck to attentioncheck to make it clear

names(pennys2r1longnodi)[5] <- "attentioncheck"

pennys2r1longnodi <- pennys2r1longnodi %>%
  mutate(headlineveracity = case_when(
    startsWith(newstype, "R") ~ "1",
    startsWith(newstype, "F") ~ "0"
    ))

##recode the measurement column

pennys2r1longnodi <- transform(pennys2r1longnodi, rescale = ave(measurement, condition, FUN = function(x) paste0((x-1)/5)))

pennys2r1longnodi_nona <- pennys2r1longnodi[!is.na(pennys2r1longnodi$measurement),]

attention1nodi <- subset(pennys2r1longnodi_nona, attentioncheck %in% c("1","2","3"))
attention2nodi <- subset(pennys2r1longnodi_nona, attentioncheck %in% c("2","3"))
attention3nodi <- subset(pennys2r1longnodi_nona, attentioncheck %in% c("3"))

@@

lm1 <- lm(rescale ~ headlineveracity + headlineveracity*condition, data = pennys2r1longnodi_nona)
summary(lm1)

@@

##change headlineveracity and rescale to numeric
pennys2r1longnodi_nona <- transform(pennys2r1longnodi_nona, 
                   headlineveracity = as.numeric(headlineveracity),
                   rescale = as.numeric(rescale))

sapply(pennys2r1longnodi_nona,mode)

pennys2nodicohenc <- subset(pennys2r1longnodi_nona, condition %in% c("0"))
pennys2nodicohent <- subset(pennys2r1longnodi_nona, condition %in% c("1"))

#condition vs measurement
cohen.d(pennys2nodicohent$Real,pennys2nodicohent$Fake, na.rm = TRUE)
cohen.d(pennys2nodicohenc$Real,pennys2nodicohenc$Fake, na.rm = TRUE)

#attention1nodi
lm2 <- lm(rescale ~ headlineveracity + headlineveracity*condition, data = attention1nodi)
summary(lm2)

stargazer(lm2, type='text')

#attention2nodi
lm3 <- lm(rescale ~ headlineveracity + headlineveracity*condition, data = attention2nodi)
summary(lm3)

stargazer(lm3, type='text')

#attention3nodi
lm4 <- lm(rescale ~ headlineveracity + headlineveracity*condition, data = attention3nodi)
summary(lm4)

stargazer(lm4, type='text')

##Try something new, see if it makes the results better
```{r, message=FALSE}
## use glm, stepwise approach to see how each factor explaining the sharing intention. The family for the model is binomial since the dependent variable is dichotomous.
glm0 <- glm(measurement ~ 1, data = pennys2r1long_nona, family = binomial(link = "logit"))

@@

glm2 <- glm(measurement ~ condition + headlineveracity, data = pennys2r1long_nona, family = binomial(link = "logit"))

glm3 <- glm(measurement ~ condition + condition*headlineveracity, data = pennys2r1long_nona, family = binomial(link = "logit"))

glm4 <- glm(measurement ~ condition + headlineveracity + attentioncheck, data = pennys2r1long_nona, family = binomial(link = "logit"))

anova(glm0,glm1,glm2,glm3,test='LR')

##looking at summary glm4, it is cleat that condition does not have a significant effect on measurement
summary(glm4)

exp(cbind(OR = coef(glm3), confint(glm3)))

glm41 <- glm(measurement ~ condition + headlineveracity + attentioncheck, data = attention1, family = binomial(link = "logit"))
glm411 <- glm(measurement ~ condition + condition*headlineveracity, data = attention1, family = binomial(link = "logit"))

summary(glm41)
summary(glm411)

glm42 <- glm(measurement ~ condition + headlineveracity + attentioncheck, data = attention2, family = binomial(link = "logit"))
glm421 <- glm(measurement ~ condition + condition*headlineveracity, data = attention2, family = binomial(link = "logit"))

summary(glm42)
summary(glm421)

glm43 <- glm(measurement ~ condition + headlineveracity, data = attention3, family = binomial(link = "logit"))
glm431 <- glm(measurement ~ condition + condition*headlineveracity, data = attention3, family = binomial(link = "logit"))

summary(glm43)
summary(glm431)

#Additional
##maybe a mixed effect models?

###create a new column that recode item number from fake and real to 1-30, with 1-15 indicate each fake items, 16-30 indicate each real items

@@

#model 1, item_id indicates repeated measurements for each item
mult1 <- lmer (measurement ~ condition + condition*headlineveracity + (1|item_id),
             data = pennys2r1long)
summary(mult1)

@@

### graph: including all
```{r, message=FALSE}

@@

@@

ggplot(p1, aes(x = condition, y = as.numeric(percent), fill = headlineveracity)) + 
  geom_bar(stat = 'identity',position = 'dodge') + 
  geom_text(
    aes(label = as.numeric (percent)), vjust = 1.5, position = position_dodge(0.9))
```

### Test (irrelevant)

### graph 2 attention check above and equal to 1
